\textbf{Emergency Service Location Optimization in a Multi-Zone District based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Fixing Header/footer

\section{Assumptions and Justifications}
\begin{description}
    \item[1. Zone to Zone Travel] \hfill \\
    	The travel times given are calculated from an optimal route from the center of the first
        zone to the center of the second. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item[2. Zone Interior Travel] \hfill \\
    	The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item[3. Zone Directional Travel] \hfill \\
    	The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item[4. Ambulance Placement] \hfill \\
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item[5. Partial Coverage] \hfill \\
        Partial ambulance coverage of a zone will be treated as incomplete even coverage over the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage. (If partial coverages from multiple ambulances sum to above the total population of a zone,
        we assume that zone is completely covered by the ambulances.)
\end{description}

@@

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as
zone-to-zone coverage.
\begin{description}

    \item[$\mathbf{A(t), B(t)}$] \hfill \\
    	Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
    	Zone-to-zone coverage of B from A
    \item[$\mathbf{v}$] \hfill \\
    	Required ambulance response time
    \item[$\mathbf{T_{AB}}$] \hfill \\
    	Travel time from A to B, given
    \item[$\mathbf{T_{BA}}$] \hfill \\
    	Travel time from B to A, given
    \item[$\mathbf{P_B}$] \hfill \\
    	Total population of B
    \item[$\mathbf{F_B(s)}$] \hfill \\
    	The probability curve for differences in travel time within B
   \item[$\mathbf{T_A}$] \hfill \\
    	Average travel time inside of A
    \item[$\mathbf{T_{A+}}$] \hfill \\
    	Average travel time in the direction of B to A inside of A
    \item[$\mathbf{T_{A-}}$] \hfill \\
    	Average travel time in the direction of A to B inside of A
   \item[$\mathbf{T_B}$] \hfill \\
    	Average travel time inside of B
    \item[$\mathbf{T_{B+}}$] \hfill \\
    	Average travel time in the direction of A to B inside of B
    \item[$\mathbf{T_{B-}}$] \hfill \\
    	Average travel time in the direction of B to A inside of B
    \item[$\mathbf{a, b}$] \hfill \\
    	Width of A and B respectively
    \item[$\mathbf{g}$] \hfill \\
    	Width of the gap between A and B
\end{description}

@@

The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$. 
$$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$
The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
$$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, have a total average travel time of $T_A$.
$$T_A = \frac{T_{A+} + T_{A-}}{2}$$
We can also write the ratio of $T_{A+}$ and $T_{A-}$, which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$.
$$\frac{T_{A+}}{T_{A-}} = \frac{T_{BA}}{T_{AB}}$$

>>>>

\section{Assumptions and Justifications}
\begin{description}
    \item[1. Zone to Zone Travel] \hfill \\
    	The travel times given are calculated from an optimal route from the center of the first
        zone to the center of the second. This excludes the possibility of reaching a zone faster
        via an indirect route from the direct, given one.
    \item[2. Zone Interior Travel] \hfill \\
    	The travel times given for travel from any zone to itself is the average
        of all the travel times of the different routes within that zone.
    \item[3. Zone Directional Travel] \hfill \\
    	The ratio between the time it takes inside a zone to travel toward a second zone,
        to the time it takes inside a zone to return from a second, is equal to the ratio
        between the travel time from the first zone to the second, and the travel time from the
        second to the first.
    \item[4. Ambulance Placement] \hfill \\
        Ambulances can only be placed in the very center of a zone. Because we do not know the
        spacial position of the zones relative to each other, we cannot consider the ambulances
        being closer to one zone or another.
    \item[5. Partial Coverage] \hfill \\
        Partial ambulance coverage of a zone will be treated as imcomplete even coverage over the entire
        zone. Because ambulances of ideal placement are unlikely to overlap in partial coverage, we assume
        that multiple ambulances will cover different areas of the zones, thus evening out coverage. (If partial coverages from multiple ambulances sum to above the total population of a zone,
        we assume that zone is completely covered by the ambulances.)
\end{description}

@@

\subsection{Zone-to-Zone Population Dynamics}
An ambulance stationed in one zone may have full, partial, or no coverage of another zone. The population
that the ambulance can cover in a second zone from a first zone (not necessarily distinct), will be hereafter referred to as zone-to-zone coverage.
\begin{description}
    \item[$\mathbf{A(t), B(t)}$] \hfill \\
    	Zones A and B are two zones separated by a gap. Each zone has a width and a population distribution
    \item[$\mathbf{Z_{AB}(t)}$] \hfill \\
    	Zone-to-zone coverage of B from A
    \item[$\mathbf{v}$] \hfill \\
    	Required ambulance response time
    \item[$\mathbf{T_{AB}}$] \hfill \\
    	Travel time from A to B, given
    \item[$\mathbf{T_{BA}}$] \hfill \\
    	Travel time from B to A, given
    \item[$\mathbf{P_B}$] \hfill \\
    	Total population of B
    \item[$\mathbf{F_B(s)}$] \hfill \\
    	The probability curve for differences in travel time within B
    \item[$\mathbf{T_{A+}}$] \hfill \\
    	Average travel time in the direction of B to A inside of A
    \item[$\mathbf{T_{A-}}$] \hfill \\
    	Average travel time in the direction of A to B inside of A
    \item[$\mathbf{T_{B+}}$] \hfill \\
    	Average travel time in the direction of A to B inside of B
    \item[$\mathbf{T_{B-}}$] \hfill \\
    	Average travel time in the direction of B to A inside of B
    \item[$\mathbf{a, b}$] \hfill \\
    	Width of A and B respectively
    \item[$\mathbf{g}$] \hfill \\
    	Width of the gap between A and B
\end{description}

@@

The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$. 
$$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$
The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
$$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, average out

the average travel time in the direction of A to B inside of B, $T_{B+}$, can be cal
